Linear vertical shear instability in astrophysical disks: a numerical study

### 2014-12-04 linear_iso.tex
new arguments on growth rate limit

For the vertical shear profile of the vertically isothermal
disk, $f(\hat{z}) =
\hat{z}\left(1+\epsilon^2\hat{z}^2\right)^{-3/2}$. If we consider
$\zmax\to\infty$,  then the growth rate is limited by the global
maximum of the vertical shear, which occurs at $\zhat
=1/\sqrt{2}\epsilon$ for the vertically isothermal disk.  
For vertical domains smaller than this height, the growth rate is
limited by $|f|$ at the vertical boundaries considered. For 
$|\epsilon\hat{z}|\ll1$ we have $f\simeq \hat{z}$, in which case we
expect growth rates to increase linearly with the vertical domain
size.

>>>>

For the vertical shear profile of the vertically isothermal
disk, $f(\hat{z}) =
\hat{z}\left(1+\epsilon^2\hat{z}^2\right)^{-3/2}$. If we consider
$\zmax\to\infty$,  then the growth rate is limited by the global
maximum of the vertical shear, which occurs at $\zhat
=1/\sqrt{2}\epsilon$.  
For vertical domains smaller than this height, the growth rate is
limited by $|f|$ at the vertical boundaries considered. For 
$|\epsilon\hat{z}|\ll1$ we have $f\simeq \hat{z}$, in which case we
expect growth rates to increase linearly with the vertical domain
size.
